BEE Paper

### 2024-04-07 paper.qmd
add spellcheck

---
title: "BEE Paper"
date: 2024-03-16
author:
  - name: Konrad Kopp
    email: konrad.kopp@stcatz.ox.ac.uk
    affiliation: University of Oxford
abstract: > 
  The abstract is currently pending
keywords:
  - Behavioral Economics
---

>>>>

---
title: "BEE Paper"
date: 2024-03-16
author:
  - name: Konrad Kopp
    email: konrad.kopp@stcatz.ox.ac.uk
    affiliation: University of Oxford
abstract: > 
  The abstract is currently pending
keywords:
  - Behavioural Economics
---
